%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Software Technical Lead} % Job title
    {The Vanguard Group} % Organization
    {Hybrid - Malvern, PA} % Location
    {Aug. 2023 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Oversee the technical delivery of a full stack team using AEM and Angular, managing Vanguard Americas FAS secure and public sites.}
        \item {Review pull requests, contribute to system architecture and implementation, develop new features and tools, and address security vulnerabilities.}
        \item {Lead strategic planning and team upskilling initiatives to ensure high-quality, secure software delivery.}
      \end{cvitems}
    }
  \cventry
    {Full Stack Engineer - Technology Leadership Program} % Job title
    {} % Organization
    {} % Location
    {Nov. 2022 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a serverless secure site that handles registration, and login for Americas investor sites.}
        \item {Led development of reporting infrastructure and data lake, enabling the business to perform client analysis.}
        \item {Managed and enhanced investor sites by developing new features, integrating with GraphQL APIs, and building new components, resulting in an improved user experience and increased product offerings.}
      \end{cvitems}
    }
  \cventry
    {DevOps Cloud Engineer - Technology Leadership Program} % Job title
    {} % Organization
    {} % Location
    {Apr. 2022 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported 5000+ containerized business applications by completing feature and escalated tickets, ensuring the smooth functioning of critical business operations and enhancing developer effeciency.}
        \item {Contributed to the enhancement of the ECS platform's stability and reliability by reducing cloud dependencies, optimizing resource utilization, and implementing best practices for container orchestration.}
        \item {Engineered a cloud-native platform insights tool that helped product teams and clients optimize their ECS costs, resulting in significant cost savings and improved resource utilization.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Backend Engineer - Technology Leadership Program} % Job title
    {} % Organization
    {} % Location
    {Aug. 2021 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Java Rest APIs that served internal consumers, specifically APIs that delivered financial fund data. Optimized queries and algorithms to decrease response times and improve application performance.}
        \item {Designed and implemented cloud-native ETL jobs and event-driven microservice architecture.}
        \item {Retired, refactored and condensed multiple REST APIs saving around 50000 USD a year.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Associate Software Engineer} % Job title
    {Pfizer} % Organization
    {Remote - Collegeville, PA} % Location
    {Aug. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to a web based micro-service data processing platform that is utilized by finance and manufacturing teams.}
        \item {Engineered a full stack web application that dynamically updates API documentation with latest releases of a set of micro-services}
        \item {Designed a front-end user interface using individual React components and built out a back-end that exposes a spring boot rest API}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
